---
title: "Text Analyis"
output: github_document
---

# Your mission

Perform text analysis.

## Okay, I need more information

Perform sentiment analysis or topic modeling using text analysis methods as demonstrated in the pre-class work and in the readings.

## Okay, I need even more information.

Do the above. Can't think of a data source?

- `gutenbergr`
- `AssociatedPress` from the `topicmodels` package
- `NYTimes` or `USCongress` from the `RTextTools` package
- Harry Potter Complete 7 Books text

```{r eval=FALSE}
if (packageVersion("devtools") < 1.6) {
  install.packages("devtools")
}

devtools::install_github("bradleyboehmke/harrypotter")
```

- [State of the Union speeches](https://pradeepadhokshaja.wordpress.com/2017/03/31/scraping-the-web-for-presdential-inaugural-addresses-using-rvest/)

- Scrape tweets using [`twitteR`](https://www.r-bloggers.com/setting-up-the-twitter-r-package-for-text-analytics/)

- [Previous URL](https://www.credera.com/blog/business-intelligence/twitter-analytics-using-r-part-1-extract-tweets/)

Analyze the text for sentiment OR topic. **You do not need to do both**.

The datacamp courses and [Tidy Text Mining with R](http://tidytextmining.com/) are good starting points for templates to perform this type of analysis, but feel free to *expand beyond these examples*.

# Timelines and Task

We will spend the next 2 weeks working on analyzing textual data in R. You will do the following:

- Start with some text based data.
- Clean data and prepare it for analysis
- Ask questions about the data
- Answer these questions with the data using tables and graphics
- Each group member must have their own unique question that they code the answer for. 

##Twitter Extraction Libraries
```{r}
#install.packages("twitteR")
#install.packages("ROAuth")
#install.packages("streamR")
library(twitteR)
library(ROAuth)
library(twitteR)
library(streamR)
library(tidyverse)

```

Check out this website (http://politicaldatascience.blogspot.com/2015/12/rtutorial-using-r-to-harvest-twitter.html)

```{r echo=FALSE}
consumer_key <- "61QAqhSHk4n1wIGkkSJd4uWYc"
consumer_secret <- "Wp5fauhEPj66F3IsTJVeAznJrq6ozNBRhrfyIweMjiLhsV4IV0"
access_token <- "903307271752605696-3YvAs5p7R7y8ASXXLCQWRUnW0veUNFB"
access_secret <- "PyrBLoT3ScECCfOsP2MlzOIW8MQW11lLsnihXu8r8k24q"

setup_twitter_oauth(consumer_key, consumer_secret, access_token, access_secret)
```
```{r}
tweets <- userTimeline("GuinnessUS", n=3200)

tw.df <- twListToDF(tweets)
```



